---
title: "MCIA_mbpca.Rmd"
author: "Anna Konstorum"
output: html_document
---

# Implement MCIA using modified mbpca function from mogsa library
# Anna Konstorum (anna.konstorum@yale.edu)


```{r load libraries}
#if (!require("BiocManager", quietly = TRUE))
#  install.packages("BiocManager")
#BiocManager::install("mogsa")

# load libraries
library(omicade4)
library(mogsa)
library(devtools)
library(RSpectra)
library(corpcor)

# example
data("NCI60_4arrays")
```

# Source additional functions from mbca library (not directly available by loading library)
```{r}
setwd('/Users/akonsto/Box Sync/MCIA_research/scripts/')
source('MCIA_mbpca_extra.R')
```


### Run MCIA
# mcia_obj$tb - the block scores
# mcia_obj$pb - the block loadings
# mcia_obj$t - the global scores
# mcia_obj$w - the weights of block scores to construct the global score

```{r}
num_comps=10
mcia_out<-mcia_mbpca(NCI60_4arrays,num_comps,preprocess='nsc',block_prep='lambda_all',
                     deflat_method='globalScore')
```

```{r}
plot(mcia_out$mcia_result$t[,1:2])
```



# Calculate global scores using MCIA block scores and weights
```{r}
gs=new_gs(mcia_out$data_prep,mcia_out$mcia_result)
```

# Check whether calculated global scores are equivalent to global scores returned by mcia_mbpca
```{r}
#block_test = blocks_out[[1]] - mcia_test$tb[[1]]
#block_test_norm = norm(block_test,type="F")

global_test = gs - mcia_out$mcia_result$t
global_test_norm = norm(global_test,type="F")
```